Posterior comparison methods

### 2022-11-01 src/explore_posterior-comparison/posterior-comparison.Rmd
Bibliography header
Small update to posterior-comparison

@@

@@

@@

# Original computing environment

@@

>>>>

Throughout this notebook we will use exemplar data from the report [`dev_sinla`](https://github.com/athowes/elgm-inf/tree/master/src/dev_sinla).

@@

## Example from Talts et al.

Let's have a go at running the `R-INLA` section from @talts2018validating as described in the GitHub repository `seantalts/simulation-based-calibration`.

```{r}
load("sbc-talts.rdata")

#' To-do...
```

@@

The `psis` function in the `loo` package takes as input some collection of importance ratios on the log scale as `log_ratios`.

@@

# Original computing environment {-}

@@

# Bibliography {-}
